AXIELL R HACKS

### 2023-02-22 _GEN_axi_Rhacks.Rmd
NM-HM, quotes corrected, misto vzniku WIP
pre-final REVISED code for MDH

# STRINGS

## Leading zeros

@@

## Split string

@@

## Remove parentheses

@@

## Remove whitespace

@@

## Create a string of multiple column values with NAs

@@

# TABLE MANIPULATIONS

## Add taxon prefix to column names

@@

## Merge two collums with not complete information

column 1 has some NAs  
column 2 has also some NAs but in different rows
TASK: create one column with merged info

@@

## Rename and rearrange columns

@@

# REGULAR EXPRESSIONS

@@

# DATABASES

@@

# JOINS

@@

# NEED TO COVER

@@

>>>>

# *GENERAL*

## S T R I N G S

### Leading zeros

@@

### Split string

@@

### Remove parentheses

@@

### Remove whitespace

@@

### Create a string of multiple column values with NAs

@@

## T A B L E S

### Add taxon prefix to column names

@@

### Merge two collums with not complete information

column 1 has some NAs  
column 2 has also some NAs but in different rows than column 1
TASK: create one column with merged info

@@

### Rename and rearrange columns

@@

## R E G E X S

@@

## D A T A B A S E S

@@

## J O I N S

@@

# *REAL TASKS*

## D A T A C E / upravit

```{r DERIVE VZNIKPTU FROM SBIRKY, warning = F, eval = F}

dopr_tab <- sbirky %>% 
  select(MINVC, Autor_S, Role_S, Datace_S, MistoVz_S) %>% 
  mutate(MEMPTY = "") %>% 
  mutate(MDATACE = Datace_S) %>% 
  # yyyy
  mutate(MDAT_Y = ifelse(str_detect(MDATACE, "_00_00"), 
                         str_replace_all(MDATACE, "_00|-00", ""), NA)) %>% 
  # mm.yyyy
  # mutate(MDAT_YM = ifelse(str_detect(MDATACE,
  #                                    "^([0-9]{4})[_]([0-9]{1})([1-9]{1})[_]00$"),
  #                                   # format(anydate(substring(MDATACE, 1, 7), "%m.%Y")), ""))
  #                                   # substring(format(anydate(MDATACE), "%m.%Y"), 1, 7), ""))
  #                                   format(anydate(MDATACE), "%m.%Y"), ""))
  # mutate(MDAT_YM = format(anydate(MDATACE), "%m.%Y")) %>%
  mutate(MDAT_YM = substring(ifelse(str_detect(MDATACE,
                                             "^([0-9]{4})[_]([0-9]{1})([1-9]{1})[_]00$"),
                                  MDATACE, ""), 1, 7)) %>%
  mutate(MDAT_YM = format(anydate(MDAT_YM), "%m.%Y")) %>%
  # dd.mm.yyyy
  mutate(MDAT_YMD = ifelse(str_detect(MDATACE,
                          "^([0-9]{4})[_]([0-9]{2})[_]([0-9]{2})$"), 
                           format(anydate(MDATACE), "%d.%m.%Y"), NA)) %>% 
  # yy leta ss stoleti
  mutate(MDAT_LETA = ifelse(str_detect(MDATACE, "^([0-9]{4})[_]XX[_]([0-9]{2})$"),
                                    paste0(substring(dopr_tab$MDATACE, 9, 9), "0. léta ",
                                           substring(dopr_tab$MDATACE, 3, 4), ". století"), NA)) %>% 
  # poloviny
  mutate(MDAT_2 = ifelse(str_detect(MDATACE, "^00\\d\\d[_]\\d2[_]XX"),
                                    paste0(substring(MDATACE, 6, 6), ". polovina ",
                                           substring(dopr_tab$MDATACE, 3, 4), ". století"), NA)) %>%
  # tretiny - NEVYSKYTUJE SE
  mutate(MDAT_3 = ifelse(str_detect(MDATACE, "^00\\d\\d[_]\\d3[_]XX"),
                                    paste0(substring(MDATACE, 6, 6), ". třetina ",
                                           substring(dopr_tab$MDATACE, 3, 4), ". století"), NA)) %>%
  # poloviny - NEVYSKYTUJE SE
  mutate(MDAT_4 = ifelse(str_detect(MDATACE, "^00\\d\\d[_]\\d3[_]XX"),
                                    paste0(substring(MDATACE, 6, 6), ". čtvrtina ",
                                           substring(dopr_tab$MDATACE, 3, 4), ". století"), NA)) %>% 
  # tretina roku
  mutate(MDAT_3r = ifelse(str_detect(MDATACE, "^\\d([1-9]{2})\\d[_]\\d3[_]XX"),
                                    paste0(substring(MDATACE, 6, 6), ". třetina roku ",
                                           substring(dopr_tab$MDATACE, 1, 4)), NA)) %>% 
  # DATACE FINAL
  mutate(MDATACE_FIN = coalesce(MDAT_Y, MDAT_YM, MDAT_YMD, MDAT_LETA, MDAT_2, MDAT_3r)) %>% 
  mutate(MDATACE_FIN = coalesce(MDATACE_FIN, MDATACE))

# *NEED TO COVER*

@@

 mutate_all( ~ str_replace_all(., pattern = ";", replacement = " ")) %>% # removes semicolons
  mutate_all( ~ str_replace_all(., pattern = "[\r\n]", replacement = " ")) #removes paragraphs
